### 2012-05-21 docs/matching_algo/matching_algo.tex
tweaked for improved circle handling
More matching algo docs

@@

\subsubsection{Termination}
\label{sec:termination}

@@

\subsubsection{Completeness}

\TODOinline{all possible ways of satisfying the postconditions are found}
\section{Testing Wrapper: Concrete Matching Only}
\label{sec:test-wrapper}

@@

@@

The previous algorithm greedily matches all concrete vertices in each iteration. However, in a situation where different concrete components of a graph are connected only by a path containing !-boxes, this could produce many spurious match candidates that only get ruled out when the connecting !-box is killed or expanded. The following algorithm removed this problem by doing concrete matching component-wise, only moving to the next component once all !-boxes connected to the currently matched concrete components have been expanded.

>>>>

\subsection{Termination}
\label{sec:termination}

@@

@@

\subsection{Completeness}
\label{sec:il-complete}

\TODO{need some restrictions on doomed(v)}
Let $f$ be a matching of the full subgraph of $L$ given by the vertices $U_C \cup U_W \cup U_N \cup \dom(m)$ into $G$ that restricts to $m$ on the vertices in $\dom(m)$.  Then we need to show that, after completion of the algorithm, one of the match states produced will agree with $f$ on vertices, except on circles.  Note that, by the argument in section \ref{sec:match-state}, this will then uniquely extend to $f$.

Since $f$ is a matching with $U_C$ in its domain (and $U_C\cap\dom(m) = \varnothing$ and $f$ restricts to $m$), there must be at least $|U_C|$ unmatched circles in $G$, and so the step where we match circles must succeed.

Invariant: the vertex map part of $f$ restricts to $m$.  $m$ is extended in two places (after circle-matching).  Each of these follows a branching point.  We need to show that in both of these places, there is a branch that will maintain this invariant.  We also need to show that none of the ``die'' branches are taken.

When adding something from $U_N$, it is clear that $f(v)$ is a valid matching for $v$, and so this is a branch that will maintain the invariant.

\TODOinline{doomed(v)}

When adding something from $U_W$, the wire starting $f(w)$ must be a valid matching for the wire starting with $w$, as the entire wire must be in the domain of $f$: if $w$ is an input or output, this is trivial.  Otherwise, there must be a wire-vertex $w'$ adjacent to $w$, and a node-vertex $n$ adjacent to $w'$.  Then $w'$ is in $U_W$, and hence in $\dom(f)$, by precondition \ref{enum:il-inv-wire-uw}, and then $n$ must be in either $P_S$ or $U_N$, by precondition \ref{enum:il-inv-reachable}, and so in $\dom(m)$ or $U_N$, and hence $n$ is in $\dom(f)$.  Once we have matched $w$ against $f(w)$, the only possible matching for $w'$ is $f(w')$, and similarly $n$ must match against $f(n)$.  If $n$ is already in $\dom(m)$, we know it maps to $f(m)$, so the matchings must agree.  So this branch maintains the invariant (and does not die).

Thus, regardless of how vertices are chosen from $P_S$, $U_N$ or $U_W$, there must be a trace that returns a match where $m$ agrees with $f$ on vertices.

\section{Testing Wrapper: Concrete Matching Only}
\label{sec:test-wrapper}

@@

Let $f:L \rightarrow G'$ be a matching of $L$ (after normalisation) onto a graph equivalent to $G$ (up to wire expansion/contraction).

following the argument in section \ref{sec:il-complete}, as if $f:L \rightarrow G'$ is a matching to a graph equivalent to $G'$, then after the concrete step (which is given an empty $m$), there must be a branch where $m$ agrees with the restriction of $f$ to all of $L$ except bare wires.  $P$ must then be empty by postcondition \ref{enum:il-postcond-P}.

@@

The previous algorithm greedily matches all concrete vertices in each iteration. However, in a situation where different concrete components of a graph are connected only by a path containing !-boxes, this could produce many spurious match candidates that only get ruled out when the connecting !-box is killed or expanded. The following algorithm removes this problem by doing concrete matching component-wise, only moving to the next component once all !-boxes connected to the currently matched concrete components have been expanded.

Here, concrete component means a connected subgraph containing no vertices in !-boxes, excluding bare wires and circles.
